Impact of Satellite Constellations on the Legacy Survey of Space and Time

### 2022-10-04 ms.tex

@@

\begin{figure}[ht!]
\epsscale{0.35}
%% XXX--matplotlib seems to like leaving a huge bounding box buffer around 
\plotone{plots/sats_slv1.pdf}
\plotone{plots/sats_slv2.pdf}
\plotone{plots/sats_ow.pdf}
\epsscale{1}
\caption{Hammer projection of the altitude and azimuth positions of our simulated satellite constellations as seen from Rubin Observatory on October 1, 2023 (sun altitude -18 degrees). Red points show un-illuminated satellites, blue points show those illuminated by the sun, and black points are illuminated and above the Rubin altitude limit. \label{fig-simulated-constellations}}
\end{figure}

>>>>

XXX--\citet{tyson20} used a very simple algorithm to try and avoid satellite streaks.  In this paper, rather than try to avoid all satellite streaks, we incorporate satellite avoidance as a component on the scheduler's Markov Decision Process, allowing us to avoid a large fraction of satellite streaks without significantly compromising the performance of the survey.

@@

\begin{figure}[ht!]
\epsscale{0.35}
\plotone{plots/sats_slv1.pdf}
\plotone{plots/sats_slv2.pdf}
\plotone{plots/sats_ow.pdf}\\
\plotone{plots/sats_slv1_late.pdf}
\plotone{plots/sats_slv2_late.pdf}
\plotone{plots/sats_ow_late.pdf}
\epsscale{1}
\caption{Hammer projection of the altitude and azimuth positions of our simulated satellite constellations as seen from Rubin Observatory on October 1, 2023 (sun altitude -18 degrees). Red points show un-illuminated satellites, blue points show those illuminated by the sun, and black points are illuminated and above the Rubin altitude limit. \label{fig-simulated-constellations} XXX--could add a second row to show how nothing is up when the sun is very low.}
\end{figure}
